### 2018-02-13 thermoelectricity/paper.tex
done tables

	\paperfig{TableTwoB}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[inner]C|[outer]}\paperoline
			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertablecheadersymbol{V_d~(\si{\volt})}\papertablecheadersymbol{I_d~(\si{\ampere})}\\
			\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertablecheaderunit{.004}{$\si{\volt}$}\papertablecheaderunit{.3}{$\si{\ampere}$}\\\paperiline
\papertableindex\papertablecval{27.9}\papertablecval{-7.0}\papertablecval{2.573}\papertablecval{12.1}\\\paperiline
\papertableindex\papertablecval{27.9}\papertablecval{-6.6}\papertablecval{2.603}\papertablecval{12.6}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-5.3}\papertablecval{2.524}\papertablecval{12.4}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-3.9}\papertablecval{2.535}\papertablecval{12.8}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-2.7}\papertablecval{2.510}\papertablecval{12.8}\\\paperiline
\papertableindex\papertablecval{28.1}\papertablecval{-1.4}\papertablecval{2.479}\papertablecval{12.9}\\\paperiline
\papertableindex\papertablecval{28.9}\papertablecval{-0.3}\papertablecval{2.752}\papertablecval{14.8}\\\paperiline
\papertableindex\papertablecval{29.4}\papertablecval{0.4}\papertablecval{2.742}\papertablecval{15.0}\\\paperiline
\papertableindex\papertablecval{28.9}\papertablecval{2.2}\papertablecval{2.447}\papertablecval{13.6}\\\paperiline
\papertableindex\papertablecval{28.5}\papertablecval{4.0}\papertablecval{2.512}\papertablecval{14.3}\\\paperiline
\papertableindex\papertablecval{28.7}\papertablecval{5.4}\papertablecval{2.542}\papertablecval{14.8}\\\paperoline
	\end{papertable}\vspace{-0.5em}}{TODO}

>>>>

	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[inner]C|[outer]}\paperoline
			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertablecheadersymbol{V_d~(\si{\volt})}\papertablecheadersymbol{I_d~(\si{\ampere})}\\
			\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertablecheaderunit{.004}{$\si{\volt}$}\papertablecheaderunit{.3}{$\si{\ampere}$}\\\paperiline
\papertableindex\papertablecval{27.9}\papertablecval{-7.0}\papertablecval{2.573}\papertablecval{12.1}\\\paperiline
\papertableindex\papertablecval{27.9}\papertablecval{-6.6}\papertablecval{2.603}\papertablecval{12.6}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-5.3}\papertablecval{2.524}\papertablecval{12.4}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-3.9}\papertablecval{2.535}\papertablecval{12.8}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-2.7}\papertablecval{2.510}\papertablecval{12.8}\\\paperiline
\papertableindex\papertablecval{28.1}\papertablecval{-1.4}\papertablecval{2.479}\papertablecval{12.9}\\\paperiline
\papertableindex\papertablecval{28.9}\papertablecval{-0.3}\papertablecval{2.752}\papertablecval{14.8}\\\paperiline
\papertableindex\papertablecval{29.4}\papertablecval{0.4}\papertablecval{2.742}\papertablecval{15.0}\\\paperiline
\papertableindex\papertablecval{28.9}\papertablecval{2.2}\papertablecval{2.447}\papertablecval{13.6}\\\paperiline
\papertableindex\papertablecval{28.5}\papertablecval{4.0}\papertablecval{2.512}\papertablecval{14.3}\\\paperiline
\papertableindex\papertablecval{28.7}\papertablecval{5.4}\papertablecval{2.542}\papertablecval{14.8}\\\paperoline
	\end{papertable}\vspace{-0.5em}}{TODO}

	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]U|[inner]U|[inner]C|[outer]}\paperoline
			\papertableindexheader\papertableuheadersymbol{V_{in}}\papertableuheadersymbol{I_{in}}\papertablecheadersymbol{V_s}\\
			\papertableuheadersymbol{(\si{\volt})}\papertableuheadersymbol{(\si{\ampere})}\papertablecheadersymbol{(\si{\volt})}\\\paperiline
\papertableindex\papertableuval{0.00}{.02}\papertableuval{0.00}{.01}\papertablecval{0.408}\\\paperiline
\papertableindex\papertableuval{0.67}{.03}\papertableuval{1.50}{.05}\papertablecval{0.396}\\\paperiline
\papertableindex\papertableuval{0.95}{.04}\papertableuval{2.12}{.06}\papertablecval{0.392}\\\paperiline
\papertableindex\papertableuval{1.16}{.04}\papertableuval{2.57}{.07}\papertablecval{0.367}\\\paperiline
\papertableindex\papertableuval{1.34}{.05}\papertableuval{2.99}{.08}\papertablecval{0.353}\\\paperiline
\papertableindex\papertableuval{1.50}{.05}\papertableuval{3.33}{.09}\papertablecval{0.336}\\\paperiline
\papertableindex\papertableuval{1.66}{.05}\papertableuval{3.6}{.1}\papertablecval{0.339}\\\paperiline
\papertableindex\papertableuval{1.78}{.06}\papertableuval{3.9}{.1}\papertablecval{0.337}\\\paperiline
\papertableindex\papertableuval{1.90}{.06}\papertableuval{4.2}{.1}\papertablecval{0.304}\\\paperiline
\papertableindex\papertableuval{2.03}{.06}\papertableuval{4.4}{.1}\papertablecval{0.281}\\\paperiline
\papertableindex\papertableuval{2.13}{.06}\papertableuval{4.7}{.1}\papertablecval{0.273}\\\paperoline
	\end{papertable}\vspace{-0.5em}}{TODO}
